---
title: "Qianying Wu's HW Website"
output: 
  html_document:
    toc: true
    toc_float: true
---

## Introduction

Welcome to Qianying's Homework page. My name is Qianying Wu. I'm a first year MS student in Biostatistics at Columbia University Mailman School of Public Health. Check my [resume](academics.html) here. In this website, you are able to find my [github page](https://github.com/BettyWu517) and my email address on the upper right corner.

## Problem 2

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(dplyr)
library(ggplot2)
library(p8105.datasets)
library(plotly)
library(flexdashboard)
```


  
```{r}
data("instacart")

instacart = 
  instacart |> 
  as_tibble()

top_aisle <- instacart |>
  count(aisle, sort = TRUE) |>
  head(10)

plot_ly(top_aisle, x = ~aisle, y = ~n, type = "bar", name = "Top 10 aisles") |>
  layout(title = "Top 10 aisles")
```

The graph presented the top 10 aisles and their counts from the Instacart Dataset. 


```{r}
# Random Sampling 
set.seed(123)  
sample_instacart <- instacart |>
  sample_n(10000)


plot_hour_dow <- sample_instacart |>
  plot_ly(y = ~order_hour_of_day,
          x = ~factor(order_dow),
          type = "box",
          color = ~factor(order_dow),
          colors = "Set3")
plot_hour_dow
```

The plot shows the boxplot in the hour of the day on which the order was placed in different day of the week on which the order was placed.


```{r}
filtered_data <- sample_instacart |>
  group_by(user_id) |>
  filter(n() >= 2)

plot_order_days <- plot_ly(data = filtered_data,
                           x = ~order_number,
                           y = ~days_since_prior_order,
                           type = "scatter",
                           mode = "markers",
                           marker = list(size = 5, opacity = 0.5),
                           text = ~paste('Order Number: ', order_number, '<br>Days since last order: ', days_since_prior_order))

plot_order_days

```

The plot shows the scatterplot, with the x axis representing the sequence number of the order for each user, and the y axis representing the number of days since the user's last order for the user_id with more than 2 entries. 


